---
title: "BIOSTAT 707 Checkpoint 1: Cohort Characterization and EDA"
author: "Jiahui Hu (jh1029)"
date: now
format:
  html:
    embed-resources: true
    toc: true
    code-fold: false
engine: knitr
execute:
  echo: true
  warning: false
  error: false
---

```{r}
#| label: setup
#| message: false

suppressPackageStartupMessages({
  library(data.table)
  library(dplyr)
  library(tidyr)
  library(readr)
  library(ggplot2)
  library(gtsummary)
  library(knitr)
})

here::i_am("checkpoint1.qmd")

data_dir     <- here::here("data")
set_a_dir    <- here::here("data", "set-a")
outcomes_csv <- here::here("data", "Outcomes-a.txt")
out_dir      <- here::here("output")
dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)

expected_n <- 4000L

theme_set(
  theme_minimal(base_size = 12) +
    theme(panel.grid.minor = element_blank())
)
```

# Reproducible data checks

```{r}
#| label: check-data

check_set_a <- function(set_a_dir, outcomes_csv, expected_n = 4000L) {
  if (!dir.exists(set_a_dir)) {
    stop(
      "Missing directory: ", set_a_dir,
      "\nExpected 4000 files under data/set-a/."
    )
  }

  if (!file.exists(outcomes_csv)) {
    stop("Missing outcomes file: ", outcomes_csv)
  }

  files <- sort(list.files(
    set_a_dir,
    pattern = "^[0-9]+\\.txt$",
    full.names = TRUE
  ))

  if (length(files) != expected_n) {
    stop(
      "Expected ", expected_n, " patient files in data/set-a/, but found ",
      length(files), "."
    )
  }

  files
}

set_a_files <- check_set_a(set_a_dir, outcomes_csv, expected_n)
```

# Load and combine the 4,000 skinny files

Each source file contains a pseudo-measurement whose `Parameter` is
`RecordID`. I use that row only to verify the filename, then remove it and keep
`RecordID` as an identifier column. This is important: if the pseudo-measurement
is allowed into `pivot_wider()`, it attempts to create a new column named
`RecordID` next to the existing identifier column and produces the duplicated
name error.

```{r}
#| label: load-set-a

time_to_minutes <- function(x) {
  pieces <- strsplit(x, ":", fixed = TRUE)
  vapply(
    pieces,
    function(z) {
      if (length(z) != 2L) return(NA_real_)
      hour <- suppressWarnings(as.numeric(z[[1]]))
      minute <- suppressWarnings(as.numeric(z[[2]]))
      if (is.na(hour) || is.na(minute)) return(NA_real_)
      60 * hour + minute
    },
    numeric(1)
  )
}

load_one_record <- function(path) {
  record_id_from_file <- suppressWarnings(as.integer(
    sub("\\.txt$", "", basename(path))
  ))

  if (is.na(record_id_from_file)) {
    stop("Could not obtain RecordID from filename: ", path)
  }

  x <- data.table::fread(
    path,
    sep = ",",
    header = TRUE,
    showProgress = FALSE
  )

  names(x) <- trimws(names(x))
  required <- c("Time", "Parameter", "Value")
  if (!all(required %in% names(x))) {
    stop("File does not contain Time, Parameter, and Value: ", path)
  }

  x[, Parameter := trimws(as.character(Parameter))]
  x[, Time := trimws(as.character(Time))]
  x[, Value := suppressWarnings(as.numeric(Value))]

  embedded_id <- x[Parameter == "RecordID", Value]
  if (length(embedded_id) != 1L ||
      is.na(embedded_id[[1]]) ||
      as.integer(embedded_id[[1]]) != record_id_from_file) {
    stop("RecordID row does not match filename in: ", path)
  }

  # Critical fix for the duplicated RecordID error.
  x <- x[Parameter != "RecordID"]
  x[, RecordID := record_id_from_file]

  x[, .(
    RecordID,
    Time,
    Minutes = time_to_minutes(Time),
    Parameter,
    Value_raw = Value
  )]
}

long_raw <- data.table::rbindlist(
  lapply(set_a_files, load_one_record),
  use.names = TRUE,
  fill = FALSE
) |>
  as_tibble()

if (anyNA(long_raw$Minutes)) {
  bad_times <- unique(long_raw$Time[is.na(long_raw$Minutes)])
  stop("Unparseable time value(s): ", paste(bad_times, collapse = ", "))
}

stopifnot(
  "RecordID must not remain as a Parameter" =
    !any(long_raw$Parameter == "RecordID"),
  "The long table must contain 4,000 records" =
    n_distinct(long_raw$RecordID) == expected_n
)
```

```{r}
#| label: load-outcomes

outcomes <- readr::read_csv(
  outcomes_csv,
  show_col_types = FALSE,
  progress = FALSE
)

# Normalize punctuation in names, e.g. SAPS-I -> SAPS_I and
# In-hospital_death -> In_hospital_death.
names(outcomes) <- gsub("[^A-Za-z0-9]+", "_", names(outcomes))
names(outcomes) <- gsub("_+$", "", names(outcomes))

required_outcomes <- c(
  "RecordID", "SAPS_I", "SOFA", "Length_of_stay",
  "Survival", "In_hospital_death"
)

if (!all(required_outcomes %in% names(outcomes))) {
  stop(
    "Outcomes-a.txt is missing required columns. Found: ",
    paste(names(outcomes), collapse = ", ")
  )
}

outcomes <- outcomes |>
  mutate(
    RecordID = as.integer(RecordID),
    In_hospital_death = as.integer(In_hospital_death)
  )

stopifnot(
  "Outcomes must contain one row per record" =
    !anyDuplicated(outcomes$RecordID),
  "Outcomes must contain 4,000 records" =
    nrow(outcomes) == expected_n,
  "Measurement and outcome IDs must agree" =
    setequal(long_raw$RecordID, outcomes$RecordID),
  "Death outcome must be coded 0/1" =
    all(outcomes$In_hospital_death %in% c(0L, 1L))
)

id_frame <- outcomes |>
  distinct(RecordID) |>
  arrange(RecordID)
```

# Data-quality decisions

The value `-1` is the dataset's missing-value sentinel, so I convert it to an
R missing value. I also screen selected variables using deliberately broad
bounds. These are data-quality bounds, not normal clinical reference ranges.
Values outside them are retained in `Value_raw`, flagged, and excluded only
from numerical summaries through `Value_clean`. This makes the handling of
questionable values auditable rather than silently deleting source rows.

```{r}
#| label: clean-values

quality_bounds <- tribble(
  ~Parameter,    ~lower, ~upper,
  "Age",             0,    130,
  "Gender",          0,      1,
  "Height",         50,    250,
  "ICUType",         1,      4,
  "Weight",         20,    400,
  "Albumin",         0,     20,
  "ALP",             0,   5000,
  "ALT",             0,  20000,
  "AST",             0,  20000,
  "Bilirubin",       0,    100,
  "BUN",             0,    300,
  "Cholesterol",     0,   1000,
  "Creatinine",      0,     30,
  "DiasABP",         0,    250,
  "FiO2",            0,      1,
  "GCS",             3,     15,
  "Glucose",         0,   2000,
  "HCO3",            0,    100,
  "HCT",             0,    100,
  "HR",              0,    300,
  "K",               0,     15,
  "Lactate",         0,     40,
  "MAP",             0,    250,
  "MechVent",        0,      1,
  "Mg",              0,     20,
  "Na",             80,    220,
  "NIDiasABP",       0,    250,
  "NIMAP",           0,    250,
  "NISysABP",        0,    300,
  "PaCO2",           0,    300,
  "PaO2",            0,    800,
  "pH",              0,     14,
  "Platelets",       0,   2000,
  "RespRate",        0,    100,
  "SaO2",            0,    100,
  "SysABP",          0,    300,
  "Temp",           25,     45,
  "TroponinI",       0,   1000,
  "TroponinT",       0,   1000,
  "Urine",           0,  10000,
  "WBC",             0,    500
)

long <- long_raw |>
  left_join(quality_bounds, by = "Parameter") |>
  mutate(
    is_sentinel_missing = !is.na(Value_raw) & Value_raw == -1,
    Value = if_else(is_sentinel_missing, NA_real_, Value_raw),
    is_nonfinite = !is.na(Value) & !is.finite(Value),
    is_implausible =
      !is.na(Value) & !is.na(lower) & !is.na(upper) &
      (Value < lower | Value > upper),
    quality_issue = case_when(
      is_nonfinite ~ "non-finite",
      is_implausible ~ "outside broad data-quality bound",
      TRUE ~ NA_character_
    ),
    Value_clean = if_else(is_nonfinite | is_implausible, NA_real_, Value)
  ) |>
  arrange(RecordID, Minutes, Parameter)

quality_summary <- long |>
  filter(!is.na(quality_issue)) |>
  count(Parameter, quality_issue, name = "flagged_rows", sort = TRUE)

if (nrow(quality_summary) == 0L) {
  quality_summary <- tibble(
    Parameter = "None",
    quality_issue = "No values were flagged",
    flagged_rows = 0L
  )
}

knitr::kable(
  quality_summary,
  caption = "Values flagged by the transparent data-quality rules"
)
```

```{r}
#| label: write-long

set_a_long <- long |>
  select(
    RecordID, Time, Minutes, Parameter,
    Value_raw, Value, Value_clean,
    is_sentinel_missing, is_implausible, quality_issue
  )

readr::write_csv(
  set_a_long,
  file.path(out_dir, "set-a_long.csv"),
  na = ""
)
```

The combined table contains `r format(nrow(set_a_long), big.mark = ",")`
measurement rows from `r n_distinct(set_a_long$RecordID)` ICU stays and
`r n_distinct(set_a_long$Parameter)` measured parameters.

# What exists at prediction time

The prediction window consists of measurements recorded during the first 48
hours of the ICU stay. The outcome variables in `Outcomes-a.txt` are used here
only to describe the cohort and investigate associations; they are not
predictors available at the prediction time. To retain timing while creating a
one-row-per-stay table, I summarize repeated measurements separately in two
landmark windows: 0--24 hours and 24--48 hours.

No outcome-based imputation or feature selection is performed in this
checkpoint. Absence of a measurement may reflect both patient physiology and
the clinical team's decision to order a test, so missingness indicators are
preserved rather than immediately imputed away.

# Baseline cohort and Table 1

```{r}
#| label: create-static

first_nonmissing <- function(x) {
  y <- x[!is.na(x)]
  if (length(y) == 0L) NA_real_ else y[[1]]
}

static_parameters <- c("Age", "Gender", "Height", "ICUType", "Weight")

static <- long |>
  filter(Parameter %in% static_parameters) |>
  arrange(RecordID, Minutes) |>
  group_by(RecordID, Parameter) |>
  summarise(Value = first_nonmissing(Value_clean), .groups = "drop") |>
  pivot_wider(
    id_cols = RecordID,
    names_from = Parameter,
    values_from = Value,
    names_repair = "check_unique"
  ) |>
  right_join(id_frame, by = "RecordID") |>
  arrange(RecordID)

table1_data <- static |>
  left_join(outcomes, by = "RecordID") |>
  mutate(
    Gender = factor(
      Gender,
      levels = c(0, 1),
      labels = c("Female", "Male")
    ),
    ICUType = factor(
      ICUType,
      levels = c(1, 2, 3, 4),
      labels = c(
        "Coronary care unit",
        "Cardiac surgery recovery unit",
        "Medical ICU",
        "Surgical ICU"
      )
    ),
    In_hospital_death = factor(
      In_hospital_death,
      levels = c(0, 1),
      labels = c("Survived", "Died")
    )
  )
```

```{r}
#| label: table1

table1_data |>
  select(
    In_hospital_death,
    Age, Gender, ICUType, Height, Weight, SAPS_I, SOFA
  ) |>
  gtsummary::tbl_summary(
    by = In_hospital_death,
    missing = "ifany",
    statistic = list(
      all_continuous() ~ "{median} ({p25}, {p75})",
      all_categorical() ~ "{n} ({p}%)"
    ),
    digits = all_continuous() ~ 1,
    label = list(
      Age ~ "Age (years)",
      Gender ~ "Sex",
      ICUType ~ "ICU type",
      Height ~ "Height (cm)",
      Weight ~ "Weight (kg)",
      SAPS_I ~ "SAPS-I",
      SOFA ~ "SOFA"
    )
  ) |>
  gtsummary::add_overall(last = FALSE) |>
  gtsummary::bold_labels() |>
  gtsummary::modify_caption(
    "**Table 1. Baseline cohort characteristics by in-hospital outcome**"
  )
```

# Outcome summary

```{r}
#| label: outcome-summary

outcome_summary <- outcomes |>
  summarise(
    Records = n(),
    Deaths = sum(In_hospital_death == 1L),
    `Death rate (%)` = 100 * mean(In_hospital_death == 1L),
    `Length of stay, median` = median(Length_of_stay, na.rm = TRUE),
    `Length of stay, Q1` = quantile(Length_of_stay, 0.25, na.rm = TRUE),
    `Length of stay, Q3` = quantile(Length_of_stay, 0.75, na.rm = TRUE),
    `SAPS-I, median` = median(SAPS_I, na.rm = TRUE),
    `SOFA, median` = median(SOFA, na.rm = TRUE)
  ) |>
  mutate(across(where(is.numeric), ~ round(.x, 1)))

knitr::kable(
  outcome_summary,
  caption = "Overall outcome and severity summary"
)
```

There were `r sum(outcomes$In_hospital_death == 1L)` in-hospital deaths among
`r nrow(outcomes)` stays, corresponding to a mortality proportion of
`r sprintf("%.1f%%", 100 * mean(outcomes$In_hospital_death == 1L))`.

```{r}
#| label: outcome-plot
#| fig-width: 7
#| fig-height: 4

outcomes |>
  count(In_hospital_death) |>
  mutate(
    Outcome = if_else(
      In_hospital_death == 1L,
      "Died in hospital",
      "Survived to discharge"
    ),
    Percent = 100 * n / sum(n)
  ) |>
  ggplot(aes(x = Outcome, y = Percent, fill = Outcome)) +
  geom_col(width = 0.65, show.legend = FALSE) +
  geom_text(
    aes(label = sprintf("%.1f%%", Percent)),
    vjust = -0.4
  ) +
  scale_y_continuous(
    limits = c(0, 100),
    expand = expansion(mult = c(0, 0.05))
  ) +
  labs(x = NULL, y = "Percent of ICU stays", title = "In-hospital outcome")
```

# Build the landmark-stacked wide table

```{r}
#| label: build-wide

# Age, Gender, Height, and ICUType are baseline descriptors. Weight can be
# repeated, so it remains in the longitudinal summaries as well as Table 1.
nonlongitudinal_parameters <- c("Age", "Gender", "Height", "ICUType")

analysis_long <- long |>
  filter(
    between(Minutes, 0, 48 * 60),
    !Parameter %in% nonlongitudinal_parameters,
    !is.na(Value_clean)
  ) |>
  mutate(
    Window = if_else(Minutes < 24 * 60, "h00_24", "h24_48")
  ) |>
  arrange(RecordID, Parameter, Window, Minutes)

summary_long <- analysis_long |>
  group_by(RecordID, Parameter, Window) |>
  summarise(
    count = n(),
    first = dplyr::first(Value_clean),
    last = dplyr::last(Value_clean),
    min = min(Value_clean),
    max = max(Value_clean),
    mean = mean(Value_clean),
    .groups = "drop"
  )

duplicate_keys <- summary_long |>
  count(RecordID, Parameter, Window, name = "rows") |>
  filter(rows > 1L)

stopifnot(
  "RecordID must never be expanded from Parameter" =
    !any(summary_long$Parameter == "RecordID"),
  "Each RecordID/Parameter/window key must be unique" =
    nrow(duplicate_keys) == 0L
)

wide_ts <- summary_long |>
  pivot_wider(
    id_cols = RecordID,
    names_from = c(Parameter, Window),
    values_from = c(count, first, last, min, max, mean),
    names_glue = "{Parameter}_{Window}_{.value}",
    names_sort = TRUE,
    names_repair = "check_unique"
  )

set_a_wide <- id_frame |>
  left_join(static, by = "RecordID") |>
  left_join(wide_ts, by = "RecordID") |>
  left_join(outcomes, by = "RecordID")

# A count of zero is meaningful; other summaries remain NA when unmeasured.
count_columns <- grep("_count$", names(set_a_wide), value = TRUE)
set_a_wide <- set_a_wide |>
  mutate(across(all_of(count_columns), ~ replace_na(.x, 0)))

stopifnot(
  "Wide table must have 4,000 rows" = nrow(set_a_wide) == expected_n,
  "Wide table must have one row per RecordID" =
    !anyDuplicated(set_a_wide$RecordID),
  "Wide-table column names must be unique" =
    !anyDuplicated(names(set_a_wide))
)

readr::write_csv(
  set_a_wide,
  file.path(out_dir, "set-a_wide.csv"),
  na = ""
)
```

The wide table has `r nrow(set_a_wide)` rows and `r ncol(set_a_wide)` columns.
It contains one row per ICU stay, baseline descriptors, outcomes, and separate
0--24-hour and 24--48-hour summaries for repeated measurements.

# Missingness using temporal information

For each six-hour block, the heat map below shows the percentage of the 4,000
stays with at least one valid observation. A blank test is therefore treated as
an absence of measurement, not as a numeric zero.

```{r}
#| label: temporal-missingness-data

time_labels <- c(
  "00-06h", "06-12h", "12-18h", "18-24h",
  "24-30h", "30-36h", "36-42h", "42-48h"
)

measured_by_block <- long |>
  filter(
    between(Minutes, 0, 48 * 60),
    !Parameter %in% nonlongitudinal_parameters,
    !is.na(Value_clean)
  ) |>
  mutate(
    Time_block = cut(
      Minutes,
      breaks = c(seq(0, 42 * 60, by = 6 * 60), 48 * 60 + 1),
      labels = time_labels,
      right = FALSE,
      include.lowest = TRUE
    )
  ) |>
  distinct(RecordID, Parameter, Time_block)

parameter_order <- measured_by_block |>
  count(Parameter, name = "observed_patient_blocks") |>
  arrange(observed_patient_blocks) |>
  pull(Parameter)

temporal_missingness <- measured_by_block |>
  count(Parameter, Time_block, name = "records_measured") |>
  complete(
    Parameter,
    Time_block = factor(time_labels, levels = time_labels),
    fill = list(records_measured = 0L)
  ) |>
  mutate(
    percent_measured = 100 * records_measured / expected_n,
    Parameter = factor(Parameter, levels = parameter_order),
    Time_block = factor(Time_block, levels = time_labels)
  )
```

```{r}
#| label: missingness-by-time
#| fig-width: 10
#| fig-height: 9

ggplot(
  temporal_missingness,
  aes(x = Time_block, y = Parameter, fill = percent_measured)
) +
  geom_tile(color = "white", linewidth = 0.15) +
  scale_fill_viridis_c(
    option = "C",
    limits = c(0, 100),
    name = "% measured"
  ) +
  labs(
    x = "Hours after ICU admission",
    y = NULL,
    title = "Availability of measurements over the first 48 hours",
    subtitle = "Each cell is the percent of stays with at least one valid value"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid = element_blank()
  )
```

# Missingness in the wide table

The next graph uses the numerical summary columns rather than the count
columns. Counts are explicitly zero when no value was measured; `first`,
`last`, `min`, `max`, and `mean` remain missing in that situation.

```{r}
#| label: wide-missingness-data

summary_value_columns <- grep(
  "_(first|last|min|max|mean)$",
  names(set_a_wide),
  value = TRUE
)

wide_missingness <- tibble(
  Variable = summary_value_columns,
  Missing_percent = 100 * vapply(
    set_a_wide[summary_value_columns],
    function(x) mean(is.na(x)),
    numeric(1)
  )
) |>
  arrange(desc(Missing_percent))

top_wide_missingness <- wide_missingness |>
  slice_head(n = 30L) |>
  mutate(Variable = factor(Variable, levels = rev(Variable)))

patient_missingness <- tibble(
  RecordID = set_a_wide$RecordID,
  Missing_percent = 100 * rowMeans(is.na(set_a_wide[summary_value_columns]))
)
```

```{r}
#| label: wide-missingness-plot
#| fig-width: 10
#| fig-height: 8

ggplot(top_wide_missingness, aes(x = Missing_percent, y = Variable)) +
  geom_col(fill = "#3B82A0") +
  scale_x_continuous(limits = c(0, 100)) +
  labs(
    x = "Missing ICU stays (%)",
    y = NULL,
    title = "Thirty most-missing summary features in set-a_wide.csv"
  )
```

```{r}
#| label: patient-missingness-plot
#| fig-width: 8
#| fig-height: 4.5

ggplot(patient_missingness, aes(x = Missing_percent)) +
  geom_histogram(binwidth = 2.5, boundary = 0, fill = "#5B8E7D", color = "white") +
  labs(
    x = "Missing summary features per ICU stay (%)",
    y = "Number of ICU stays",
    title = "Patient-level burden of missingness"
  )
```

# Is missingness informative?

To examine whether measurement decisions carry outcome information, I compare
the death rate between stays in which each variable was ever measured during
the first 48 hours and stays in which it was never measured. This is a
descriptive association, not a causal effect: ordering a test may reflect
illness severity, clinical workflow, or both.

```{r}
#| label: missingness-outcome-association

dynamic_parameters <- sort(unique(analysis_long$Parameter))

measurement_flags <- long |>
  filter(
    between(Minutes, 0, 48 * 60),
    Parameter %in% dynamic_parameters,
    !is.na(Value_clean)
  ) |>
  distinct(RecordID, Parameter) |>
  mutate(ever_measured = TRUE)

measurement_grid <- tidyr::crossing(
  RecordID = id_frame$RecordID,
  Parameter = dynamic_parameters
) |>
  left_join(measurement_flags, by = c("RecordID", "Parameter")) |>
  mutate(ever_measured = replace_na(ever_measured, FALSE)) |>
  left_join(
    outcomes |> select(RecordID, In_hospital_death),
    by = "RecordID"
  )

death_by_measurement <- measurement_grid |>
  group_by(Parameter, ever_measured) |>
  summarise(
    n = n(),
    deaths = sum(In_hospital_death == 1L),
    death_rate = mean(In_hospital_death == 1L),
    .groups = "drop"
  ) |>
  complete(
    Parameter,
    ever_measured = c(FALSE, TRUE),
    fill = list(n = 0L, deaths = 0L, death_rate = NA_real_)
  )

death_association <- death_by_measurement |>
  pivot_wider(
    id_cols = Parameter,
    names_from = ever_measured,
    values_from = c(n, deaths, death_rate),
    names_sep = "_",
    names_repair = "check_unique"
  ) |>
  mutate(
    death_rate_difference = death_rate_TRUE - death_rate_FALSE
  ) |>
  arrange(desc(abs(death_rate_difference)))

readr::write_csv(
  death_association,
  file.path(out_dir, "missingness_outcome_association.csv"),
  na = ""
)

death_association |>
  filter(n_FALSE >= 20L, n_TRUE >= 20L) |>
  transmute(
    Parameter,
    `Never measured, n` = n_FALSE,
    `Measured, n` = n_TRUE,
    `Death rate, never measured (%)` = round(100 * death_rate_FALSE, 1),
    `Death rate, measured (%)` = round(100 * death_rate_TRUE, 1),
    `Difference (percentage points)` =
      round(100 * death_rate_difference, 1)
  ) |>
  slice_head(n = 20L) |>
  knitr::kable(
    caption = paste(
      "Variables with the largest absolute difference in death rate by",
      "whether they were measured (groups with at least 20 stays)"
    )
  )
```

These differences show that missingness is not simply random noise. They do
not establish that measuring a variable changes mortality. More plausibly,
test ordering and monitoring intensity encode information about patient
severity, ICU workflow, and treatment decisions. In later predictive work,
missingness indicators may therefore be useful features, but all imputation
and feature construction must be learned inside each training fold to avoid
information leakage.

# Output validation

```{r}
#| label: validate-output

required_outputs <- c(
  file.path(out_dir, "set-a_long.csv"),
  file.path(out_dir, "set-a_wide.csv")
)

stopifnot(
  "Required CSV outputs were not created" = all(file.exists(required_outputs)),
  "Long output is empty" = file.info(required_outputs[[1]])$size > 0,
  "Wide output is empty" = file.info(required_outputs[[2]])$size > 0
)

tibble(
  Output = basename(required_outputs),
  Rows = c(nrow(set_a_long), nrow(set_a_wide)),
  Columns = c(ncol(set_a_long), ncol(set_a_wide)),
  `Size (MB)` = round(file.info(required_outputs)$size / 1024^2, 2)
) |>
  knitr::kable(caption = "Required derived data products")
```

# AI-use statement

<!-- IMPORTANT: Edit this paragraph so it truthfully describes what YOU did. -->

I used OpenAI Codex to help diagnose a duplicated-column-name error in
`pivot_wider()`, draft boilerplate for reproducible file loading and validation,
and explain several R operations. The main benefit was faster debugging and a
clearer set of defensive checks. The main risk was that generated code could
make incorrect assumptions about variable meaning or silently mishandle
missing values. I reviewed the code line by line, checked the data dimensions
and identifiers, inspected the generated tables and figures, and rendered the
document using the locked pixi environment. I revised the generated suggestions
where needed and remain responsible for the analysis and interpretation.

# Session information

```{r}
#| label: session-info

sessioninfo::session_info()
```
